\subsection{Day 1} \label{sec:day1}

The daily meeting took place as planned at 11:00 PST.

Bias, Flat, and Dark sequences were acquired.  A clear problem, L3 fogging, was 
noted and resulted in the replacement of the N2 bottle.  It was noted that 
fogging was clearing and flats on subsequent nights should show a change.  

Transfers showed problems with roughly 25s per file (CCD).  The $\sim$30 exposure 
required O(1.5 hours) to reach the USDF.  On arrival problems were detected with
the ingestion of data.  The culprit was that two processes were trying to ingest 
incoming files (one linking them with a deprecated file path).  Once transfers 
completed, data repositories were regenerated fixing the issue.  

Processing proceeded rapidly.  Jobs were submitted using parallelism over 9 CCDs
making up the ComCam raft.  Total processing time was O(15 minutes) using 10 cores.
There were problems with calibration ingestion (the CALIB area does not have 
permissions to allow group access).  It is suspected that this has caused preliminary 
calibration based on early ComCam tests from a few week prior to be used in the 
reduction of the new calibration data but current provenance did not show
which calibraitons were used.

QA was performed with notebooks shared.  This analysis demonstrated that the 
proper calibrations were not used.  

\subsubsection{Discussion}
We discussed how to implement change in infrastructure to support the current
Butler Gen2 usage of calibrations (group write permissions were extended for the
interim).  Further discussions about Gen2 vs. Gen3 and the level of sophistication
to plan for the next rehearsal.  

